Malacology: A Programmable Storage System

### 2017-03-08 paper/3_challenges.tex
paper: camera-ready template and url fixes
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

The main challenge of designing a programmable storage system is choosing the
right internal abstractions and picking the correct layers for exposing them.
\oldcomment{In this paper, we do not present an exhaustive list of possible
internal abstractions nor do we contend that the abstractions we choose provide
the best trade-offs for all applications.} \newcomment{A programmable storage
is not defined by what abstractions are exposed, rather a programmable storage
system adheres to the design approach of exposing interfaces so administrators
can have better control of the storage system. The interfaces presented in this
paper are abstractions that we found useful for building our prototype services
ZLog and Mantle, yet they may not provide the best trade-offs for all
higher-level services.} \addressesissue{2} For example, if consensus is
correctly exposed one could implement high-level features like versioning,
serialization, or various flavors of strongly consistent data management on
top; but perhaps a low-level consensus interface is suited well for a
particular set of applications.  These questions are not answered in this paper
and instead we focus on showing the feasibility of building such a system,
given advances in the quality and robustness of today's storage stacks.

>>>>

The main challenge of designing a programmable storage system is choosing the
right internal abstractions and picking the correct layers for exposing them.
\oldcomment{In this paper, we do not present an exhaustive list of possible
internal abstractions nor do we contend that the abstractions we choose provide
the best trade-offs for all applications.} \newcomment{A programmable storage system
is not defined by what abstractions are exposed, rather a programmable storage
system adheres to the design approach of exposing interfaces so administrators
can have better control of the storage system. The interfaces presented in this
paper are abstractions that we found useful for building our prototype services
ZLog and Mantle, yet they may not provide the best trade-offs for all
higher-level services.} \addressesissue{2} For example, if consensus is
correctly exposed one could implement high-level features like versioning,
serialization, or various flavors of strongly consistent data management on
top; but perhaps a low-level consensus interface is suited well for a
particular set of applications.  These questions are not answered in this paper
and instead we focus on showing the feasibility of building such a system,
given advances in the quality and robustness of today's storage stacks.

### 2017-03-08 paper/9_conclusion.tex
paper: camera-ready template and url fixes
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Programmable storage is a viable method for eliminating duplication of complex
error-prone software used as workarounds for storage system deficiencies. We
propose that systems expose their services in a safe way allowing application
developers to customize system behavior to meet their needs while not
sacrificing correctness. To illustrate the benefits of this approach we
presented Malacology, a programmable storage system that facilitates the
construction of new services by re-purposing existing subsystem abstractions of
the storage stack.

@@

>>>>

Programmable storage is a viable method for eliminating duplication of complex
error-prone software used as workarounds for storage system deficiencies. We
propose that systems expose their services in a safe way allowing application
developers to customize system behavior to meet their needs while not
sacrificing correctness. To illustrate the benefits of this approach we
presented Malacology\footnote{\url{http://programmability.us}}, a
programmable storage system that facilitates the construction of new services
by re-purposing existing subsystem abstractions of the storage stack.

@@

\acks

We thank the EuroSys reviewers for their hard work, attentiveness, and
genuinely helpful suggestions. We also thank Mahesh Balakrishnan for
championing and shepherding the paper. This work was partially funded by the
Center for Research in Open Source
Software\footnote{\url{http://cross.ucsc.edu}}, the DOE Award
DE-SC0016074, and the NSF Award 1450488.

\textbf{Note}: this paper follows The Popper
Convention~\cite{jimenez_popper_2016}. The Popper
Convention\footnote{\url{http://falsifiable.us}} is equivalent to
the ACM's Result and Artifiact Review and Badging procedures.
\includegraphics[width=3.5mm]{figures/popper.png}

### 2017-03-08 paper/paper.tex
paper: camera-ready template and url fixes
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\documentclass[preprint]{sigplanconf-eurosys}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{pifont}
\usepackage{color}
\usepackage{comment}

@@

\title{Malacology: A Programmable Storage System}
%\authorinfo{Paper ID: 165}          {Total Pages: 12}
\authorinfo{Michael A. Sevilla, Noah Watkins, Ivo Jimenez, \\Peter Alvaro, Shel Finkelstein, Jeff LeFevre, Carlos Maltzahn}
           {\{msevilla, jayhawk, ivo\}@soe.ucsc.edu, \{palvaro, shel, jlefevre, carlosm\}@ucsc.edu}
\date{}
\begin{document}

@@

  \input{./0_abstract}
  \input{./1_intro}
  \input{./2_application_specific_storage_stacks}
  \input{./3_challenges}
  \input{./4_malacology_a_programmable_storage_system}
  \input{./5_services_built_on_malacology}
  \input{./6_evaluation}
  \input{./7_future_work}
  \input{./8_related_work}
  \input{./9_conclusion}

\bibliography{paper}
\bibliographystyle{plain}

>>>>

%-----------------------------------------------------------------------------
%
%               Template for sigplanconf LaTeX Class
%
% Name:         sigplanconf-template.tex
%
% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
%               file for SIGPLAN conference proceedings.
%
% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
%               sigplanconf-guide.pdf
%
% Author:       Paul C. Anagnostopoulos
%               Windfall Software
%               978 371-2316
%               paul@windfall.com
%
% Created:      15 February 2005
% Source:       http://www.sigplan.org/Resources/Author/
%-----------------------------------------------------------------------------

\documentclass[numbers]{sigplanconf}

% The following \documentclass options may be useful:

% preprint       Remove this option only once the paper is in final form.
%  9pt           Set paper in  9-point type (instead of default 10-point)
% 11pt           Set paper in 11-point type (instead of default 10-point).
% numbers        Produce numeric citations with natbib (instead of default author/year).
% authorversion  Prepare an author version, with appropriate copyright-space text.

\usepackage{amsmath}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{pifont}
\usepackage{color}
\usepackage{comment}

@@

\newcommand{\cL}{{\cal L}}

\begin{document}

\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

\conferenceinfo{CONF'yy}{Month d--d, 20yy, City, ST, Country}
\copyrightyear{20yy}
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}\reprintprice{\$15.00}
\copyrightdoi{nnnnnnn.nnnnnnn}

% For compatibility with auto-generated ACM eRights management
% instructions, the following alternate commands are also supported.
%\CopyrightYear{2016}
%\conferenceinfo{CONF'yy,}{Month d--d, 20yy, City, ST, Country}
%\isbn{978-1-nnnn-nnnn-n/yy/mm}\acmPrice{\$15.00}
%\doi{http://dx.doi.org/10.1145/nnnnnnn.nnnnnnn}

% Uncomment the publication rights used.
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}  % default
%\setcopyright{rightsretained}

\titlebanner{This is a draft!}        % These are ignored unless
\preprintfooter{short description of paper}   % 'preprint' option specified.

\title{Malacology: A Programmable Storage System}

\authorinfo{Michael A. Sevilla, Noah Watkins, Ivo Jimenez, \\Peter Alvaro, Shel Finkelstein, Jeff LeFevre, Carlos Maltzahn}
           {University of California, Santa Cruz}
           {\{msevilla, jayhawk, ivo\}@soe.ucsc.edu, \{palvaro, shel\}@ucsc.edu, \{jlefevre, carlosm\}@soe.ucsc.edu}

@@

\input{./0_abstract}

% 2012 ACM Computing Classification System (CSS) concepts
% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011008</concept_id>
<concept_desc>Software and its engineering~General programming languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003752.10010124.10010138.10010143</concept_id>
<concept_desc>Theory of computation~Program analysis</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~General programming languages}
\ccsdesc[300]{Theory of computation~Program analysis}
% end generated code

% Legacy 1998 ACM Computing Classification System categories are also
% supported, but not recommended.
%\category{CR-number}{subcategory}{third-level}[fourth-level]
%\category{D.3.0}{Programming Languages}{General}
%\category{F.3.2}{Logics and Meanings of Programs}{Semantics of Programming Languages}[Program analysis]

\keywords
keyword1, keyword2

\input{./1_intro}
\input{./2_application_specific_storage_stacks}
\input{./3_challenges}
\input{./4_malacology_a_programmable_storage_system}
\input{./5_services_built_on_malacology}
\input{./6_evaluation}
\input{./7_future_work}
\input{./8_related_work}
\input{./9_conclusion}

% The 'abbrvnat' bibliography style is recommended.
\bibliographystyle{abbrvnat}

% The bibliography should be embedded for final submission.
\bibliography{paper}
